---
title: "Lab 01 - Hello R"
author: "Jonathan Trattner"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: journal
    highlight: monochrome
---

```{r include = FALSE}
knitr::opts_chunk$set(fig.width = 6, fig.height = 6)
```

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

Basedo n the text it has 1846 rows and 3 columns. The variables are the dataset, indicating which dataset the data comes from, and x/y.

### Exercise 2

The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.

First let's plot the data in the dino dataset:

```{r plot-dino}
datasaurus_dozen %>%
  filter(dataset == "dino") %>%
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
datasaurus_dozen %>%
  filter(dataset == "dino") %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Add code and narrative as needed. Note that the R chunks are labelled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, clean up the narrative by removing these instructions.

Blah blah blah...

```{r plot-star}
datasaurus_dozen %>%
  filter(dataset == "star") %>%
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

I'm some text, you should replace me with more meaningful text...

```{r cor-star}
datasaurus_dozen %>%
  filter(dataset == "star") %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.

```{r plot-circle}
datasaurus_dozen %>%
  filter(dataset == "circle") %>%
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
datasaurus_dozen %>%
  filter(dataset == "circle") %>%
  summarize(r = cor(x, y))
```

### Exercise 5

```{r plot-all}
datasaurus_dozen %>%
  ggplot(aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) + 
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```
